---
title: "Random-networks"
author: "Ashleigh Novak"
date: "3/7/2021"
output: html_document
---

Methods are used in:

1) Novak, A. J., Becker, S. L., Finn, J. T., Danylchuk, A. J., Pollock, C. G., Hillis-Starr, Z., Jordaan, A. 2020. Inferring residency and movement patterns of horse-eye jack Caranx latus in relation to a Caribbean marine protected area acoustic telemetry array. Animal Biotelemetry. 8:12. https://doi.org/10.1186/s40317-020-00199-8

2) Novak, A. J., Becker, S. L., Finn, J. T., Pollock, C. G., Hillis-Starr, Z., Jordaan, A. 2020. Scale of biotelemetry data influences ecological interpretations of space and habitat use in yellowtail snapper Ocyurus chrysurus. Marine and Coastal Fisheries: Dynamics, Management, and Ecosystem Science 12:364–377.

Code to generate random networks. Note, this was done for each fish.

```{r}
#Set up your empty dataframe
RandomStatsFISHID = data.frame(ID = 1:10000,
                     DegreeCount = NA,
                     ClosenessCount = NA,
                     BetweenCount = NA)

#Set # of random networks to be generated
n=10000

#Loop to fill in empty data frame with random data
# 78 is the number of receivers the fish could have possibly visited
# 23616 is the number of filtered detections for this fish

for (i in 1:n) {
  MySequence = sample(1:78, size = 23616, replace = T)
  #glimpse(MySequence)
  MySeqLag = MySequence[2:23616]
  #glimpse(MySeqLag)
  RandFromToDF2 = data.frame(From=MySequence[1:23615], To=MySeqLag)
  MyTable2 = table(From=RandFromToDF2$From, To = RandFromToDF2$To)
  EL_SuperRandom = MoveEdgeList.nm.nz(MyTable2)
  EL_SuperRandom$weight = as.numeric(EL_SuperRandom$weight)
  RandomMovementGraph23593 = graph.data.frame(EL_SuperRandom, directed = T)
   #plot(RandomMovementGraph23593)
   #is.igraph(RandomMovementGraph23593)
  RandomStatsFISHID$DegreeCount[i] = centralization.degree(RandomMovementGraph23593)$centralization
  RandomStatsFISHID$ClosenessCount[i] = centralization.closeness(RandomMovementGraph23593)$centralization
  RandomStatsFISHID$BetweenCount[i] = centralization.betweenness(RandomMovementGraph23593)$centralization
}
```

#Test significance of your random network against the fish's

```{r}

hist(RandomStatsFISHID$DegreeCount, xlim = c(0,0.45))
range(RandomStatsFISHID$DegreeCount) 

#MovegraphFISHID is the movement graph or network (I created mine using the package igraph) for the fish 
value = centralization.degree(MovegraphFISHID)$centralization 
abline(v=(centralization.degree(MovegraphFISHID)$centralization), col="red", lwd=3)

#Coefficient of variation

#Random
mean(RandomStatsFISHID$DegreeCount) 
sd(RandomStatsFISHID$DegreeCount) 

# Test for significance!
wilcox.test(RandomStatsFISHID$DegreeCount, mu = X , alternative = "two.sided")
#where X is the number specifying an optional parameter used to form the null hypothesis

#Real
value = centralization.degree(MovegraphFISHID)$centralization 
quantile(RandomStatsFISHID$DegreeCount, probs = c(0.975))
```

